Differential Expression - HBCC - DLPFC - Dx

### 2020-05-19 individual-cohorts/HBCC_DLPFC_DE.Rmd
covar sampleid as rowname

# Get covariates
COVAR_ID = "syn22082458"
ALL_USED_IDs = c(ALL_USED_IDs, COVAR_ID)
COVARIATES = downloadFile(COVAR_ID)

@@

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx", "ageOfDeath", "RIN", "IntronicRate", "IntragenicRate", "IntergenicRate")
random_effect <- c("Reported_Gender")
```

>>>>

# Get covariates
COVAR_ID = "syn22082458"
ALL_USED_IDs = c(ALL_USED_IDs, COVAR_ID)
COVARIATES = downloadFile(COVAR_ID) %>% 
  column_to_rownames(var = "SampleID")

@@

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx", "scale(ageOfDeath)", "scale(RIN)", "scale(IntronicRate)", "scale(IntragenicRate)", "scale(IntergenicRate)")
random_effect <- c("Reported_Gender")
```
